Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-09-06 doc/manuscript/manuscript.Rmd
fix locus_table -> loc_table

The number of observed alleles per locus ranged from two to 10 with an average of `r signif(Amean, 3)` (Table \@ref(tab:locus-stats)).
Locus `r locus_table$Locus[locus_table$allele==2]`, which contained only 2 alleles, showed low values of both *h* (`r signif(locus_table$Hexp[locus_table$allele==2], 3)`) and evenness (`r signif(locus_table$Evenness[locus_table$allele==2], 3)`), indicating that there was one dominant allele present. 
Analysis of the haplotype accumulation curve showed no clear plateau (Supplemental Information), indicating that we would likely obtain more multilocus haplotypes if we were to genotype more loci.

>>>>

The number of observed alleles per locus ranged from two to 10 with an average of `r signif(Amean, 3)` (Table \@ref(tab:locus-stats)).
Locus `r loc_table$Locus[loc_table$allele==2]`, which contained only 2 alleles, showed low values of both *h* (`r signif(loc_table$Hexp[loc_table$allele==2], 3)`) and evenness (`r signif(loc_table$Evenness[loc_table$allele==2], 3)`), indicating that there was one dominant allele present. 
Analysis of the haplotype accumulation curve showed no clear plateau (Supplemental Information), indicating that we would likely obtain more multilocus haplotypes if we were to genotype more loci.
